### 2023-06-06 manuscript.Rmd
Update manuscript.Rmd
Co-authored-by: Aaron Peikert <aaron.peikert@posteo.de>

In sum, we are thankful to @gartner2022responsible for highlighting the importance of research software contributions as scientifically valuable products.
We believe the current proposal should aim to better reflect the distinction between rigor and impact for software, similar to the guidelines proposed to evaluate journal articles.
To this end, we suggest a more fine-grained assessment of rigor, and put emphasis on the merit statement, in which software authors should argue in how far their project impacted other scientific endeavors.
Last, we hope to arrive at an evaluation scheme that incentivizes the development of scientific open-source software.
Note that the requirements of a given academic position should guide the weighting of research software when evaluating and selecting candidates. In some cases, research software development may be central to a position and therefore a requirement (such as when hiring professors of statistics or research methods), but in other cases, we hope that research software development activities at least are considered as research output comparable to published papers.

>>>>

In sum, we are thankful to @gartner2022responsible for highlighting the importance of research software contributions as scientifically valuable products.
We believe the current proposal should aim to better reflect the distinction between rigor and impact for software, similar to the guidelines proposed to evaluate journal articles.
To this end, we suggest a more fine-grained assessment of rigor, and put emphasis on the merit statement, in which software authors should argue in how far their project impacted other scientific endeavors.
Last, we hope to arrive at an evaluation scheme that incentivizes the development of scientific open-source software.
Note that the requirements of a given academic position should guide the weighting of research software when evaluating and selecting candidates.
In some cases, research software development may be central to a position and, therefore, a requirement (such as when hiring professors of statistics or research methods), but in other cases, we hope that research software development activities at least are considered as research output comparable to published papers.
